---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# pctSantiago

## Introduction

The goal of pctSantiago is to create a proof-of-concept or prototype of a 'Pedalea' web application to help prioritise active transport policies and investment where they are most urgently needed.
The starting point is the Propensity to Cycle Tool web app and research project hosted at http://www.pct.bike/

In terms of project workflow, the simplest approach is to push everything into this README.Rmd file, with specific scripts going directly into the repo's route directory (this is not an R package, yet, so no need for an R folder) and data going in the releases.

In terms of software, we will use the following packages:

```{r}
# install.packages("remotes")
pkgs_cran = c(
  "sf" # spatial package
)
remotes::install_cran(pkgs_cran)
pkgs_github = c(
  "ropensci/stplanr",
  "ITSLeeds/pct",
  "GIScience/openrouteservice-r"
)
remotes::install_github(pkgs_github)
```

## Input data



## Desire line analysis


## Route generation and analysis




## Cycling uptake




## Route networks and recommendations

This section aims to show how recommendations can be generated.

